A Certified Interpreter for the List Machine Benchmark

### 2020-06-20 papers/SBLP2020/paper.tex
More changes on text. Infrastructure to measure compilation time.

We implemented 15 tasks from the list machine benchmark in the Agda programming language.
The total number of lines for each task is summarized in the next table.

@@

>>>>

We implemented 14 tasks from the list machine benchmark in the Agda programming language.
The total number of lines for each task is summarized in the next table.

@@

The total time for parsing and proof checking our Agda implementation was around 10 seconds 
on a machine with a Intel Core I7 1.7 GHz, 8GB RAM running Mac OS X 10.15.5.
